### 2020-12-07 doc/thesis/chapters/fm_radio.tex
some more table of content

  \section{Up-Downconversion to/from RF}

  \section{Frequency Modulation}
  see literature/Present\_lec6\_AM\_FM.pdf\\
  see lectures out of HSD/ESD

@@

%%%%%%%%%%%%%%%%%%%%
\chapter{High-Level Synthesis}
  \section{Introduction / State of the Art}
  \section{Functionality (high level code to HDL)}
  \section{Variants}
    \subsection{C++}
    \subsection{SystemC}
  \section{Advantages / Disadvantages}

%%%%%%%%%%%%%%%%%%%%
\chapter{Implementation}
  \section{Matlab Simulation}
  in fixed point, close to hardware level algorithm

@@

>>>>

  \section{Modulation from Baseband to RF}
  \section{Modulation from RF to Baseband}

  \section{Frequency Modulation (FM)}
  see literature/Present\_lec6\_AM\_FM.pdf\\
  see lectures out of HSD/ESD
    \subsection{Mathematical description}
    \subsection{Frequency Band, Channel allocation/distribution}

@@

%%%%%%%%%%%%%%%%%%%%
\chapter{High-Level Synthesis}
  \section{Introduction / State of the Art}
  \section{Functionality (transform high-level code to HDL)}
  \section{Language Support}
    \subsection{C++}
    \subsection{SystemC}
  \section{Coding}
    \subsection{Compiler Directives (\#pragma's)}
    \subsection{Data types}
    \subsection{Functions}
    \subsection{Loops}
    \subsection{Conditional statements}
  \section{Advantages / Disadvantages}
    easy and much faster to get complex HDL code, such as image/video processing, through libraries like OpenCV. However, it is less optimized, and a developer still needs to have a strong hardware background, to be able to understand what is being generated in hardware from x lines of code in HLS/Cpp.

%%%%%%%%%%%%%%%%%%%%
\chapter{Implementation}
  \section{Matlab/Python Model}
  in fixed point, close to hardware level algorithm

@@

  \section{Common Testbench}
    \subsection{Architecture (same tb for VHDL and HLS-generated HDL)}
    \subsection{Framework cocotb, with ghdl compiler}
        Instantiate both HDL models in the testbench.\\
        Display a direct comparison of outputs in graphs. This is practical, since the cocotb framework runs in python and graphs can be generated using Python's matplotlib.

  \section{Develop HLS compiler independent code (optional)}
    \subsection{Challenges}
     Different compilers use different \#pragmas, etc.\\
     The \#pragmas need to be within the code, at the appropriate positions, which makes it difficult to write compiler independent code....

### 2020-12-07 doc/thesis/chapters/introduction.tex
some more table of content

@@

\begin{enumerate}
  \item GnuRadio (?)
  \item Matlab
  \item HLS\\
      Implementation targeting Xilinx' ZedBoard.\\
      Optionally: \\
      Intel as a comparison (synth only, no HW) - "How platform-independent is HLS?"
  \item VHDL
\end{enumerate}
\vspace{.5 cm}
Compare:
- Implementation effort (difficulty)
- Implementation time
- Usefulness on Target Systems (uC, SoC, RasPi, etc)
- others?

>>>>

%%%%%%%%%%%%%%%%%%%%%%%
\section{Motivation}

FM is a common RF signal that's available everywhere.\\
The demodulated signal is an audio signal, that can be listened to. This is subjectively more attractive than a generic data stream.

%%%%%%%%%%%%%%%%%%%%%%%
\section{Broadcast Radio}
Evolution from AM to FM because of certain advantages, etc.\\
Explain FM usage/existence nowadays (geographical; frequencies; devices; new standard DAB, etc)

\section{Goal}
put all knowledge that was accumulated during studies (HSD, ESD, mention subjects such as DSP) together in a project.\\
practical usage of DSP in an FPGA\\
develop an FM receiver and explain it, so that it can be followed in a tutorial with an affordable budget in hardware.\\
show multiple ways of how to implement the same thing, in different levels of abstraction. Weigh each ways' field of application, efficiency and applicability.

%%%%%%%%%%%%%%%%%%%%%%%
% NOTES:
%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{enumerate}
  \item GnuRadio (?)
  \item Matlab/Python
  \item HLS\\
      Implementation targeting Xilinx' ZedBoard.\\
      Optionally: \\
      Intel as a comparison (synth only, no HW) - "How platform-independent is HLS?"
  \item VHDL
\end{enumerate}
\vspace{.5 cm}

Compare:
- Implementation effort (difficulty)
- Implementation time
- Usefulness on Target Systems (uC, SoC, RasPi, etc)
- others?
